TO FIND

### 2013-05-22 ms.tex
Phil's section on spatial graphs

%========================================================%
\section{Network representation of landscapes}
% PDP

Entités discrètes --> réseaux

% Table 1: main descriptors of spatial networks. Column 1: Name of the metric; Column 2: Definition
% We might want to distinguish network level versus node-level metrics.

@@

%========================================================%
\section{Discussion}
% TP

@@

New questions

Making the theory operational
	- how to parameterize neutral models
	- making predictions for specific landscapes
	-

Distribution attendue des espèces dans un paysage: utiliser la théorie neutre pour avoir un attendu (différents de la méthode classique de permutation)

- Utiliser les déviations locales pour comprendre le rôle de la sélection

- Approche par réseau: vers une approche qui intègre la variance des mécanismes de coexistence

Our results point to an important, although often overlooked, consequence of
neutral dynamics. Emerging properties of a community (i.e. the number of
species, but also their spatial distribution and co-occurence in different local
patches), are affected by the dispersal structure.

- Importance de la structure du paysage sur les propriétés émergentes
	- importance relative de species sorting et drift va dépendre de l'organisation du paysage
	- prédiction
	- rôle de la distribution de degrés
-

>>>>

%========================================================%
\section{Network representation of landscapes}

A network is a discrete mathematical object made of two sets: a set of
vertices (or nodes) $V$ and a set of edges $E$ connecting the vertices
\cite{new10}. The term ``graph'' is often preferred in computer science and
mathematics \cite{gro06}, with graph algorithms being an important and active
area of research \cite{sed01}. A network is a combinatorial object: it is
used to study how discrete entities are connected and how they combine
together to create complex structures. They are used to study molecules, food
webs, social networks, or even the relationship between variables in
statistics \cite{wri21,new10}. We are especially interested in spatial
networks, a special kind of network mixing the combinatorial properties of
networks with a topological space \cite{kob94}. Thus, the vertices in a
spatial graph are embedded in some other space, most often the two or three-
dimensional Euclidean space. This object brings a rich representation to
spatial ecology and is particularly suited for systems of lakes and rivers, which can
easily be represented by vertices and edges. There are two notions of
distance in spatial networks. Euclidean distance represents the geographical
distance between the vertices $(i, j)$, i.e.: $\sqrt{(x_i - x_j)^2 + (y_i - y_
j)^2}$. Geodesic distance is the distance in the graph space, i.e.: the
length of the shortest path \cite{dij59}. For example, two lakes could be
very close on a map (short Euclidean distance) but if they are not directly
linked by a river the geodesic distance could be great.

For simulations, spatial networks can easily be generated with the random
geometric graph algorithm \cite{sed01}. In this algorithm, all vertices are
assigned to a position in some two-dimensional space, most often the unit
square. Then, all pairs of vertices within some threshold Euclidean distance $r$
are connected with an edge. The resulting networks have the desirable
property of locality: if a vertex $A$ is connected to two vertices $B$ and $C$.
then $B$ and $C$ are more likely to be connected than two random vertices.
Random geometric networks have been extensively studied \cite{app97a,app97
b,app02a,app02b,pen03} and we provide a R function to generate them. We also
provide the code for another structure that we call the geometric tree of
doom. It builds a tree from the shortest path tree \cite{dij59} of a vertex in
a random geometric network. This random geometric tree of doom looks like a
lake connected by rivers to a series of smaller lakes.

Spatial graphs are increasingly popular in spatial ecology and conservation
biology, where patterns of connections can be used to study and influence the
flow of organisms \cite{min07,fal07,min08,gar08,urb09,dal10}. In the neutral
theory, networks were pioneered by Economo and Keitt \cite{eco08, eco10}.
They used networks to study how different spatial structures influenced
diversity. They were also used to study how the spatial structure influenced
nonsympatric speciation \cite{des12,des12b}.

% Table 1: main descriptors of spatial networks. Column 1: Name of the metric; Column 2: Definition
% We might want to distinguish network level versus node-level metrics.
Concepts
  Path A sequence of edges forming a sequence of vertices.
  Connection Two vertices are connected iff there is a path between them.
  Geodesic distance Length of the shortest path between two vertices.
Network-level metrics
  Order Total number of vertices.
  Size Total number of edges.
  Connectivity A measure of robustness: the minimum number of elements to remove
                          to isolate the vertices.
  Components The number of connected subsets.
Vertex-level metrics
  Degree The number of edges of a vertex.
  Closeness centrality Average geodesic distance between a vertex and all other vertex.
  Eigenvector centrality A measure of centrality based on the concept that connection to
                          highly connected vertices are more important.
  Betweenness centrality The number of shortest paths from all vertices to all others that
                          pass through that vertex.

@@

%========================================================%
\section{Discussion}

@@

Network approach brings spatial variation in coexistence mechanisms; emergent properties
	- role of the degree distribution

Making the theory operational
	- how to parameterize neutral models
	- making predictions for specific landscapes

Working with more realistic landscapes

How to add other types of interactions
	- Wootton: variation arises from unaccounted interactions
